Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-05-06 paper.tex
editing of Sect 3 finished

{\bf Energy in compressive modes} The total turbulence energy is typically $\sim 15-70\%$ of the thermal energy in a cluster \citep{vazza11}; it rises rapidly during a merger. The compressible component is $\sim 20-40\%$ of the total turbulent energy, and shows more rapid temporal variations compared to the compressible component \citep{2013ApJ...771..131B,2015ApJ...800...60M}. It is worth noting that in the subsonic regime of the solar wind \citep{yao11,howes12}, as well as most idealized calculations of turbulent driving, there is relatively little energy in the fast mode. For instance, the fidiucial simulations of \citet{lynn14} with a sonic Mach number ${\mathcal M}_{\rm s} \sim 0.35$ and a plasma beta factor of $\beta \sim 1$ show that 50\%, 45\%, 5\% of the turbulent energy density is in the Alfv{\'e}n, slow, and fast modes, respectively. For higher $\beta \sim 3-10$, they find that the proportion of energy in fast modes drops to $< 1\%$, while the fraction of energy in the slow mode remains roughly the same. Similarly, \citet{kowal10} find that the fast mode is highly subdominant (see their Table 2); for the run most relevant to cluster conditions ${\mathcal M}_{\rm s} \sim 0.7, \beta \sim 10$, they find $\sim 42\%, 6\%$ of turbulent energy in slow and fast modes respectively. These simulations are roughly consistent with theoretical estimates of $U_{\rm fast}/U_{\rm slow} \sim {\mathcal M}_{\rm s}^{2}/{\mathcal M}_{\rm A}$ \citep{cho03}. By contrast, MHD simulations of galaxy clusters find a large fraction ($\sim 25$\%) of turbulent energy in fast modes \citep{2013ApJ...771..131B}. This is likely due to the compressive nature of turbulent driving (transonic infall and merger), whereas idealized simulations tend to use incompressible solenoidal driving and allow compressive fluctuations to develop on their own.

@@

It can be shown that the particle pitch-angle averaged
momentum-diffusion coefficient of isotropic particles that couple to
fast magnetosonic modes via TTD resonance is \citep[][
  Eqn. 47]{brunetti07}:
\begin{eqnarray}
  D_{pp}(p,t) = \frac{\upi}{16} \frac{p^2}{\rho c}
  \left\langle\frac{\beta |B_k|^2}{16 \upi \,W}\right\rangle
  I_\theta
  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
\label{eq:dpp}
\end{eqnarray}
where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
is the speed of light. The energy density $W$ of a mode in a
magnetized plasma stems from both electromagnetic fields and resonant
particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
beta-weighted magnetic-to-total energy density saturates to $\langle\beta
|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
\citealt{brunetti07}). The pitch angle of the CR momentum with the
magnetic field orientation is given by $\theta$, and
\begin{equation}
  \label{eq:I_theta}
  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
    |\cos \theta | }}
\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
\end{equation}
Here $\Vph$ is the phase velocity of the fast magnetosonic waves
given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
in \cite{brunetti07}, we initially assume that the velocity of
turbulent eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the
cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
Tab.~\ref{tab:timescales} for more details).

@@

We adopt a simplified isotropic MHD turbulent spectrum based on
Kraichnan's picture for the fast modes per elemental range $dk$ of the
form
\begin{equation}
  \label{eq:Wk}
  \mathcal{W}(k) =
\sqrt{2/7\,I_0\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
\end{equation}
for $k_0<k<k_\rmn{cut}$. Here we adopt an injection scale of the
turbulence, $k_0= 2\upi/\lambda_0$ with $\lambda_0 =100~\mbox{kpc}$,
that is in line with previous work
\citep{2006MNRAS.366.1437S,brunetti07,brunetti11}. Note that this
length scale defines an eddy turn-over time
$\tau_{\rmn{eddy}}\sim2\upi\lambda_0/V_0\sim1.2$~Gyr with
$V_0=500\,\rmn{km~s}^{-1}$, characteristic of a merger event.

@@

@@

During reacceleration, the CRps increase their normalization
approximately by the factor
\begin{equation}
  \label{eq:Creacc}
  \delta C_\rmn{reacc.} \sim 
  \exp{\left[\frac{(2+\alpha)(\alpha+1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,,
\end{equation}
if injection and cooling are neglected. The reaccelerated CRs depend
exponentially on $\tau_D\sim 1/D_{pp}$ as long as $\tau_D \lesssim
\tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration of
reacceleration of the merger which we assume to be 650~Myrs long.

% --- section: Analytical Results and discussion --- %
\section{Parameter space exploration with spherical models}
\label{sect:param_comp}
In this paper we rely on several critical parameters describing
relatively unknown non-thermal physics in the ICM. Here we try to
explore the robustness of our models to the most critical parameters
related to turbulence and CRs.

\subsection{Methodology}
In this section we develop a simplified framework that will be used to
test the robustness of our models with respect to the critical
parameters for CRs and turbulence in Section~\ref{sect:param_comp}. In
order to quickly explore parameter space, we we solve the
Fokker-Planck equation in static spherical shells for injection,
reacceleration, and losses of the CRs, i.e., we neglect the Lagrangian
trajectories during the re-acceleration time.  Once the CRs have been
reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we calculate the
radio emission and compare the profile and spectra for different
parameterizations.

We adopt both the density \citep{1992A&A...259L..31B} and temperature
profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
X-ray observations of the Coma cluster. They are given by:
\begin{eqnarray}
n_e &=& \frac{n_0}{\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{1.125}}\nonumber\\
k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32}\,,
\end{eqnarray}
with $n_0=3.4\times10^{-3}\,\rmn{cm}^{-3}$.  The virial and core radii
of Coma are given by $R_{200} = 2300\,\rmn{kpc}$
\citep{2002ApJ...567..716R} and $R_{\rmn{c}} = 294\,\rmn{kpc}$,
respectively.

The bulk of the CRps are injected by relatively low Mach number shocks
and parameterized by $f_\rmn{p,inj}(p) =
C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where $\alpha_\rmn{inj}\approx
2.5$ in our simulations. The CRps approximately trace the thermal gas
with $C_\rmn{inj} \propto \eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
\citep{pinzke10,2016MNRAS.459...70V}, where the normalization is fixed
by the injected CR energy in the last 650~Myrs. Our simulations show
that it roughly make up 0.03\% of the thermal energy inside the virial
radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{p,0} \propto \frac{\int_p^\infty f_\rmn{p,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalization by requiring
$\int_0^{R_{200}}\eps_\rmn{p,0}
\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.003$. Note that the injected energy in the last 650 Mys is smaller
by about a factor of 10 in comparison to the cumulative CR energy
injected over the entire cosmological history of the cluster.
Similarly, the initial CRe distribution is given by the steady state
between cooling (Coulomb, inverse Compton, and synchrotron) and
injection of secondary CRes from $f_\rmn{p,0}$. We also include the
continuous injection of secondary CRes during $\tau_\rmn{cl}$. The
compressible turbulence responsible for reaccelerating both the CRps
and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_{\rmn{e}}
T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_{pp}$ is calculated
for each radial bin using Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All
parameters and assumptions are similar to what is used for our
simulated cluster.

@@

Figure~\ref{fig:param_comp} shows their
impact on radio emission. We find that the level of turbulence
($X_\rmn{tu}$) has a large impact on both radio spectra and profiles,
while the parameter $\alpha_\rmn{tu}$ that determines the spatial
profile of turbulence mainly influence the radio profiles. As
expected, the radio profiles flatten significantly with a flatter
turbulent profile. A higher amount of turbulent energy also flatten
the radio profile, where the reason being that the steep profiles of
injected CRs have less impact on the radio emission for an increasing
reacceleration efficiency. Interestingly, assumptions about CRs have
less impact on radio emission. This can be understood by looking at
the scaling of parameters to the reacceleration timescale, where
$\tau_\rmn{D} \propto 1/D_\rmn{pp} \propto 1/X_\rmn{tu}^2$. From
Eqn.~\ref{eq:Creacc} we see that the CRps with a spectral index of
$\alpha_\rmn{p}\approx2.5$ approximately gain a factor $\Delta
C_\rmn{reacc.} \sim
\exp{\left[1.7\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}$ during
reacceleration if injection and cooling are neglected. The CRes gain a
similar factor from reacceleration, however in the region around
$0.1\,R_{200}$ the Coulomb cooling timescale
($\tau_\rmn{coul}\approx0.01\,\rmn{Gyr}$) is much shorter than
$\tau_\rmn{D}\approx0.6\,\rmn{Gyr}$, hence $\Delta C_\rmn{reacc.}$
will be greatly reduced for the electrons. The spatial region is
important when we derive the radio spectrum, since in order to compare
to observations we integrate the CR profile out to $\sim
0.2\,R_{200}$. For $X_\rmn{tu}=0.2$ and $\alpha_\rmn{tu}=0.8$ we find
that $\Delta C_\rmn{reacc.} \sim 10$. This is confirmed by the top
panels in Fig.~\ref{fig:param_comp}. Increasing the level of
turbulence to $X_\rmn{tu}=0.3$, gives us a $\Delta C_\rmn{reacc.}
\sim 100$, which is roughly confirmed by same figures. The factor 2-3
difference in the figure is due to the shorter reacceleration
timescale that increase the contribution from reaccelerated CRes that
would otherwise cool away on a much shorter timescale. Hence we
conclude that the radio emission is much more sensitive to the
exponential dependence on compressible turbulence than the linear
dependence on injected CRs.

We can also derive a lower critical level of turbulence where
reacceleration is negligible, while it rises sharply above this
threshold. We define the threshold by $\Delta C_\rmn{reacc.}  \lesssim
2$, which gives us an $X_\rmn{thres,tu} = \left(\frac{0.04\,\log(2)
}{1.7}\frac{\tau_\rmn{D}}{\tau_\rmn{cl}}\right)^{0.5} \approx 0.08$
for $\tau_\rmn{D} = 0.6\,\rmn{Gyr}$. This threshold is also seen in
the top panels of figure~\ref{fig:param_comp}. For instance, for
$X_\rmn{tu}\gtrsim0.08$, a factor two change in $X_\rmn{tu}$ changes
the radio surface brightness by a factor $\sim 10-100$. In principle
this threshold behavior allows us to provide a strict lower bound on
turbulence in radio halos. An even more stringent bound on
$X_\rmn{tu}$ can be inferred from combining radio observations with
the gamma-ray observations (see section~\ref{sect:radio_spec}).

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aI0.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aI0.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aCR.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aCR.eps}
   \end{center}
\end{minipage}
\caption{Sensitivity of radio emission in Coma cluster to critical
  parameters. {\it Left panels} show the radio surface brightness
  profiles. We compare profiles at 352~MHz \citep[blue lines and
    crosses,][]{brown11} to predicted emission from Fermi-II
  reaccelerated CR electrons populations (black lines). {\it Right
    panels} show radio synchrotron spectra. The green crosses are
  compiled from observations \citet{2010PhDT.......259P}, while the
  black lines show predicted emission from reaccelerated CR
  electrons. The upper panels show the sensitivity to the level of
  turbulence ($X_\rmn{tu}$), middle panels show the impact of
  different turbulent profiles ($\alpha_\rmn{tu}$), and lower panels
  show the dependence on spatial distributions of initial and injected
  CRs ($\alpha_\rmn{CR,spat}$). We adopt the following fiducial values
  for parameters that are not varied in each panel: $X_\rmn{tu}=0.2$,
  $\alpha_\rmn{tu}=0.8$, and $\alpha_\rmn{CR,spat}=1.0$. Note that the
  radio emission is much more sensitive to assumptions about turbulent
  parameters than CRs.}
  \label{fig:param_comp}
\end{figure*}

@@

The profile of injected turbulence depends on the details of the
merger such as time during the merger, the impact parameter, the
merger mass ratio, and the degree of cluster anisotropy
\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
assume that it scales with the thermal energy density to some
power. Hence we assume volumetric injection rate of turbulent energy,
$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
normalization by requiring that the turbulent energy in compressible
modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
radio halo.\footnote{Simulations show that the compressible modes
  contribute a factor $0.2-0.4$ to the total turbulent energy
  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
  total turbulent energy, which can be decomposed into a slenoidal and
  compressible component, is typically $\sim15-70$\% of the thermal
  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
  our adopted value of $X_\rmn{tu}$.} In this work we investigate
different spatial models for injected turbulence. With the above
choice of normalization, the turbulent energy density becomes
$\eps_\rmn{turb} \propto
\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
\Mprimary (see Figure~\ref{fig:turb} for visualization).

@@

{\bf Acknowledgments.} We thank Josh Wiener for discussions on CR
streaming. We are also grateful to Lawrence Rudnick for discussion on
uncertainties in the 1.4 GHz radio data. Finally, we thank Fabio
Zandanel for recalculating gamma-ray limits and Gianfranco Brunetti
for useful discussions. A.P. is grateful to the Swedish research
council for financial support. S.P.O. thanks NASA grant NNX12AG73G for
support. C.P.~gratefully acknowledges financial support of the Klaus
Tschira Foundation.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-0.7cm}

>>>>

{\bf Energy in compressive modes} The total turbulence energy is typically $\sim 15-70\%$ of the thermal energy in a cluster \citep{vazza11}; it rises rapidly during a merger. The compressible component is $\sim 20-40\%$ of the total turbulent energy, and shows more rapid temporal variations compared to the compressible component \citep{2013ApJ...771..131B,2015ApJ...800...60M}. It is worth noting that in the subsonic regime of the solar wind \citep{yao11,howes12}, as well as most idealized calculations of turbulent driving, there is relatively little energy in the fast mode. For instance, the fiducial simulations of \citet{lynn14} with a sonic Mach number ${\mathcal M}_{\rm s} \sim 0.35$ and a plasma beta factor of $\beta \sim 1$ show that 50\%, 45\%, 5\% of the turbulent energy density is in the Alfv{\'e}n, slow, and fast modes, respectively. For higher $\beta \sim 3-10$, they find that the proportion of energy in fast modes drops to $< 1\%$, while the fraction of energy in the slow mode remains roughly the same. Similarly, \citet{kowal10} find that the fast mode is highly subdominant (see their Table 2); for the run most relevant to cluster conditions ${\mathcal M}_{\rm s} \sim 0.7, \beta \sim 10$, they find $\sim 42\%, 6\%$ of turbulent energy in slow and fast modes respectively. These simulations are roughly consistent with theoretical estimates of $U_{\rm fast}/U_{\rm slow} \sim {\mathcal M}_{\rm s}^{2}/{\mathcal M}_{\rm A}$ \citep{cho03}. By contrast, MHD simulations of galaxy clusters find a large fraction ($\sim 25$\%) of turbulent energy in fast modes \citep{2013ApJ...771..131B}. This is likely due to the compressive nature of turbulent driving (transonic infall and merger), whereas idealized simulations tend to use incompressible solenoidal driving and allow compressive fluctuations to develop on their own.

@@

It can be shown that the particle pitch-angle averaged
momentum-diffusion coefficient of isotropic particles that couple to
fast magnetosonic modes via TTD resonance is \citep[][
  Eqn. 47]{brunetti07}:
\begin{eqnarray}
  D_{pp}(p,t) = \frac{\upi}{16} \frac{p^2}{\rho c}
  \left\langle\frac{\beta |B_k|^2}{16 \upi \,W}\right\rangle
  I_\theta
  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
\label{eq:dpp}
\end{eqnarray}
where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
is the speed of light. The energy density $W$ of a mode in a
magnetized plasma stems from both electromagnetic fields and resonant
particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
beta-weighted magnetic-to-total energy density saturates to $\langle\beta
|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
\citealt{brunetti07}). The pitch angle of the CR momentum with the
magnetic field orientation is given by $\theta$, and
\begin{equation}
  \label{eq:I_theta}
  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
    |\cos \theta | }}
\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
\end{equation}
Here $\Vph$ is the phase velocity of the fast magnetosonic waves
given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
in \cite{brunetti07}, we initially assume that the velocity of
turbulent eddies is $\varv_0\approx 0.47 c_\rmn{s}$ throughout the
cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
Tab.~\ref{tab:timescales} for more details).

@@

We adopt a simplified isotropic MHD turbulent spectrum based on
Kraichnan's picture for the fast modes per elemental range $dk$ of the
form
\begin{equation}
  \label{eq:Wk}
  \mathcal{W}(k) =
\sqrt{2/7\,I_0\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
\end{equation}
for $k_0<k<k_\rmn{cut}$. Here we adopt an injection scale of the
turbulence, $k_0= 2\upi/\lambda_0$ with $\lambda_0 =100~\mbox{kpc}$,
that is in line with previous work
\citep{2006MNRAS.366.1437S,brunetti07,brunetti11}. Note that this
length scale defines an eddy turn-over time
$\tau_{\rmn{eddy}}\sim2\upi\lambda_0/\varv_0\sim1.2$~Gyr with
$\varv_0=500\,\rmn{km~s}^{-1}$, characteristic of a merger event.

@@

The profile of injected turbulence depends on the details of the
merger such as time during the merger, the impact parameter, the
merger mass ratio, and the degree of cluster anisotropy
\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
assume that it scales with the thermal energy density to some
power. Hence we assume volumetric injection rate of turbulent energy,
$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
normalization by requiring that the turbulent energy in compressible
modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
radio halo.\footnote{Simulations show that the compressible modes
  contribute a factor $0.2-0.4$ to the total turbulent energy
  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
  total turbulent energy, which can be decomposed into a slenoidal and
  compressible component, is typically $\sim15-70$\% of the thermal
  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
  our adopted value of $X_\rmn{tu}$.}

@@

\SPO{the derivation of the following is not transparent, could you expand?}
During reacceleration, the CRps increase their normalization
approximately by the factor
\begin{equation}
  \label{eq:Creacc}
  \delta C_\rmn{reacc.} \sim 
  \exp{\left[\frac{(2+\alpha)(\alpha+1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,,
\end{equation}
if injection and cooling are neglected. The reaccelerated CRs depend
exponentially on $\tau_D\sim 1/D_{pp}$ as long as $\tau_D \lesssim
\tau_\rmn{cl}$, where $\tau_\rmn{cl}$ represent the duration of
reacceleration of the merger which we assume to be 650~Myrs long.

% --- section: Analytical Results and discussion --- %
\section{Parameter space exploration with spherical models}
\label{sect:param_comp}
In this paper we rely on several critical parameters describing
relatively unknown non-thermal physics in the ICM. Here we develop a
simplified framework that will be used to explore the robustness of
our models to the most critical parameters related to turbulence and
CRs.

\subsection{Methodology}

As we have seen before, the resulting radio-emitting CRe distribution
depends on compressible turbulence (which sets the level of
reacceleration) and the distribution of pre-existing CRs. Hence we
vary parameters describing the amount of energy contained in
turbulence relative to the thermal energy, $X_{\rm tu}$, the spatial
profile of turbulence as parametrized by $\alpha_{\rm tu}$, as well as
the spatial CR profile that we will parametrize by $\alpha_{\rm CR,
  spat}$ (see below).  In order to quickly explore this parameter
space, we solve the Fokker-Planck equation in static spherical shells
for injection, reacceleration, and losses of the CRs, i.e., we neglect
the Lagrangian trajectories during the re-acceleration time.  Once the
CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we
calculate the resulting radio emission and compare the emission
profiles and spectra as we vary one parameter at the time relative to
our fiducial model.

We adopt both the density \citep{1992A&A...259L..31B} and temperature
profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
X-ray observations of the Coma cluster,
\begin{eqnarray}
n_e &=& n_0\,\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{-1.125},\nonumber\\
k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32},
\end{eqnarray}
with $n_0=3.4\times10^{-3}\,\rmn{cm}^{-3}$.  The virial and core radii
of Coma are given by $R_{200} = 2300\,\rmn{kpc}$
\citep{2002ApJ...567..716R} and $R_{\rmn{c}} = 294\,\rmn{kpc}$,
respectively.

The bulk of the CRps are injected by relatively low Mach number shocks
and parameterized by $f_\rmn{p,inj}(p) =
C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where $\alpha_\rmn{inj}\approx
2.5$ in our simulations. The CRps approximately trace the thermal gas
with $C_\rmn{inj} \propto \eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
\citep{pinzke10,2016MNRAS.459...70V}, where the normalization is fixed
by the injected CR energy in the last 650~Myrs. Our simulations show
that it approximately amounts to 0.03\% of the thermal energy inside
the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{p,0} \propto \frac{\int_p^\infty f_\rmn{p,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalization by requiring
$\int_0^{R_{200}}\eps_\rmn{p,0}
\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.003$. Note that the injected energy in the last 650 Mys is smaller
by about a factor of 10 in comparison to the cumulative CR energy
injected over the entire cosmological history of the cluster.
Similarly, the initial CRe distribution is given by the steady state
between cooling (Coulomb, inverse Compton, and synchrotron) and
injection of secondary CRes from $f_\rmn{p,0}$. We also include the
continuous injection of secondary CRes during $\tau_\rmn{cl}$. The
compressible turbulence responsible for reaccelerating both the CRps
and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_{\rmn{e}}
T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_{pp}$ is calculated
for each radial bin using Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All
parameters and assumptions are similar to what is used for our
simulated cluster (see Sect.~\ref{sec:results}).

@@

Figure~\ref{fig:param_comp} shows the impact of turbulence and the
spatial distribution of CRs on the radio emission.  We find that the
level of turbulence ($X_\rmn{tu}$) has a large impact on both radio
spectra and profiles, while the parameter $\alpha_\rmn{tu}$ that
determines the spatial profile of turbulence mainly influences the
radio profiles. As expected, the radio profiles flatten significantly
with a flatter turbulent profile. A larger amount of turbulent energy
also flattens the radio profile, because the steep profiles of
injected CRs have less impact on the radio emission for an increasing
reacceleration efficiency.

Interestingly, the spatial profile of CRs has a smaller impact on the
radio emission. This can be understood by looking at the scaling of
parameters to the reacceleration timescale, where $\tau_\rmn{D}
\propto 1/D_\rmn{pp} \propto 1/X_\rmn{tu}^2$. From
Equation~\ref{eq:Creacc} we see that the CRps with a spectral index of
$\alpha_\rmn{p}\approx2.5$ approximately gain a factor $\delta
C_\rmn{reacc.} \sim \exp{(1.7\,\tau_\rmn{cl}/\tau_\rmn{D})}$ during
reacceleration if injection and cooling are neglected. The CRes gain a
similar factor from reacceleration, however in the region around
$0.1\,R_{200}$ the Coulomb cooling timescale
($\tau_\rmn{Coul}\approx0.01\,\rmn{Gyr}$) is much shorter than
$\tau_\rmn{D}\approx0.6\,\rmn{Gyr}$, hence $\delta C_\rmn{reacc.}$
will be greatly reduced for the electrons. The spatial region is
important when we derive the radio spectrum, since in order to compare
to observations we integrate the CR profile out to $\sim
0.2\,R_{200}$. For $X_\rmn{tu}=0.2$ and $\alpha_\rmn{tu}=0.8$ we find
that $\delta C_\rmn{reacc.} \sim 10$. This is confirmed by the top
panels in Fig.~\ref{fig:param_comp}. Increasing the level of
turbulence to $X_\rmn{tu}=0.3$, gives us a $\delta C_\rmn{reacc.}
\sim 100$, which is roughly confirmed by same figures. The factor 2-3
difference in the figure is due to the shorter reacceleration
timescale that increase the contribution from reaccelerated CRes that
would otherwise cool away on a much shorter timescale. Hence we
conclude that the radio emission is much more sensitive to the level
of compressible turbulence through an exponential dependence.  In
contrast, the radio emission only depends linearly on the density of
injected CRs.

We can also derive a critical level of turbulence below which
reacceleration is negligible. Above this threshold, reacceleration
becomes increasingly more efficient. We define the threshold by
$\delta C_\rmn{reacc.}  \lesssim 2$, which gives us an
$X_\rmn{thres,tu} = \sqrt{0.04\,\log(2)/1.7 \times
  \tau_\rmn{D}/\tau_\rmn{cl}} \approx 0.08$ for $\tau_\rmn{D} =
0.6\,\rmn{Gyr}$. The existence of such a threshold can also manifested
in the top panels of Fig.~\ref{fig:param_comp}. For
$X_\rmn{tu}\gtrsim0.08$, changing $X_\rmn{tu}$ by a factor of two
changes the radio surface brightness by a factor of $\sim 10-100$. In
principle this threshold behavior allows us to provide a strict lower
bound on turbulence in radio halos. An even more stringent bound on
$X_\rmn{tu}$ can be obtained by combining radio observations with
the gamma-ray observations (see Section~\ref{sect:radio_spec}).

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aI0.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aI0.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aCR.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aCR.eps}
   \end{center}
\end{minipage}
\caption{Sensitivity of radio emission in Coma cluster to critical
  parameters. The left-hand panels show the radio surface brightness
  profiles. We compare profiles at 352~MHz \citep[blue
    crosses,][]{brown11} to predicted emission from Fermi-II
  reaccelerated CR electrons populations (black lines). The right-hand
  panels show radio synchrotron spectra. The green crosses are
  compiled from observations \citep{2010PhDT.......259P}, while the
  black lines show predicted emission from reaccelerated CR
  electrons. The upper panels show the sensitivity to the level of
  turbulence ($X_\rmn{tu}$), the middle panels show the impact of
  different turbulent profiles ($\alpha_\rmn{tu}$), and the lower
  panels show the dependence on spatial distributions of initial and
  injected CRs ($\alpha_\rmn{CR,spat}$). We adopt the following
  fiducial values for our model, $X_\rmn{tu}=0.2$,
  $\alpha_\rmn{tu}=0.8$, and $\alpha_\rmn{CR,spat}=1.0$ and vary each
  parameter separately in each row of panels. We find that the radio
  emission is much more sensitive to the level of turbulence while it
  depends less senstively to the spatial distribution of CRs.}
  \label{fig:param_comp}
\end{figure*}

@@

In this work we investigate
different spatial models for injected turbulence. With the above
choice of normalization, the turbulent energy density becomes
$\eps_\rmn{turb} \propto
\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
\Mprimary (see Figure~\ref{fig:turb} for visualization).

@@

{\bf Acknowledgments.} We thank Josh Wiener for discussions on CR
streaming. We are also grateful to Lawrence Rudnick for discussion on
uncertainties in the 1.4 GHz radio data. Finally, we thank Fabio
Zandanel for recalculating gamma-ray limits and Gianfranco Brunetti
for useful discussions. A.P. is grateful to the Swedish research
council for financial support. S.P.O. thanks NASA grant NNX12AG73G for
support. C.P.~acknowledges support by the European Research Council
under ERC-CoG grant CRAGSMAN-646955 and by the Klaus Tschira
Foundation.
